Learning and comparing functional connectomes between populations

### 2012-09-04 paper.tex
Take notes to fill in outline

\begin{abstract}
    We are the champion... of the world
\end{abstract}

\begin{keyword}
    Functional connectivity, connectome, group study, effective
    connectivity
\end{keyword}

@@

@@

\subsection{Defining regions}

\subsection{Estimating connections}

@@

\subsection{Mass-univariate approaches}

\subsection{Modeling between-connection dependences}

@@

\subsection{From correlations to structural equation modeling}

@@

\subsection{Matching model complexity to data}

>>>>

\begin{abstract}
    We are the champion... of the world

    Scope: rest and task-based studies. But focusing on fMRI.
\end{abstract}

\begin{keyword}
    Functional connectivity, connectome, group study, effective
    connectivity, fMRI, resting-state
\end{keyword}

@@

Review paper giving technical guidelines.

@@

%------------------------------------------------------------------------------
\subsection{Defining regions}

Different strategies: 
dense/sparse: covering a large fraction of the
brain or not, hard vs soft boundaries.

\paragraph{Regions from atlases}

AAL, Harvard-oxford

\paragraph{Defining regions from the literature}
Meta-analysis

\paragraph{FMRI-based function definition}
Distinction between activation and rest.
Activation: thresholding GLM maps, or using spheres around the activation
peak.
Rest: ICA-based approaches \cite{kiviniemi2009} XXX: cite Grecius paper.
\cite{varoquaux2011}

%------------------------------------------------------------------------------
\subsection{Estimating connections}

% Disclaimer: focus on correlation/second order statistics?

\paragraph{Signal extraction}

Once again separate task from rest

Task: beta time-series, and more recent stuff, \emph{e.g.} by Mumford and
Poldrack.

Rest: importance of confounds. Filtering + and detrending.

\paragraph{Correlation and partial correlations}

Correlation, shrinkage of correlation, partial correlation, sparse iCov.

@@

%------------------------------------------------------------------------------
\subsection{Mass-univariate approaches}

%------------------------------------------------------------------------------
\subsection{Modeling between-connection dependences}

@@

%------------------------------------------------------------------------------
\subsection{From correlations to structural equation modeling}

@@

%------------------------------------------------------------------------------
\subsection{Matching model complexity to data}
